Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-22 paper/ms.tex
update paper

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{epdparams_vs_time.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		Timeseries of ``external parameters'' for a representative
			star over one sector.
			{\it Top}: Instrumental raw magnitude (with a particular
		aperture size), as a function of time.  {\it Second and third from
			top}: $x$ and $y$ centroid positions as a function of time.
		Continuing in order are the CCD temperature, the $(s,d,k)$ shape
		parameters, and the measured background value.
		Most of the apparent variability is instrumental.
		\label{fig:external_parameter_timeseries}
	}
\end{figure}

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.44\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    The variability in flux is sometimes correlated with variability in
	``external'' parameters, shown here for a representative star
    over two orbits.  {\it Top}: Instrumental raw magnitude (with a
    particular aperture size), as a function of time.  
    Continuing in order are $x$ and $y$ centroid positions as a functions of
    time, the $(s,d,k)$ PSF shape parameters,
    the CCD temperature,  and the measured background value.
    Differential aberration affect the centroid position over the span of each orbit.
    Momentum dumps are
    marked with vertical dashed lines, and affect the measured shapes of stars.
		\label{fig:external_parameter_timeseries}
	}
\end{figure}
